Multiphysics Core Dynamics Simulation Using the Improved Quasi-Static Method

### 2016-10-28 doc/M&C_2017/MC2017_Summary.tex
final review

IQS is a powerful tool for reactor simulation, it has the capability of greatly reducing computation time while retaining accuracy of relevant quantities.  The goal of this summary is to showcase IQS's performance with multi-physics simulation, as well as techniques to improve its performance.  The technique focused on incorporating a new time scale in IQS for feedback quantities and PRKE parameters.  The results when IQS is applied to the temperature feedback model of the LRA benchmark showed that incorporating a middle time scale for temperature had significant impact on IQS performance.

A full report of this topic will include applying step doubling time adaptation to the LRA benchmark and analyzing IQS performance.  It is also intended to include IQS application to a full core TREAT model to analyze performance with a more complex problem.  It is also possible to include IQS application to the Godiva model as to analyze performance with a structural feedback problem \cite{CritSafetyHandbook}.

>>>>

IQS is a powerful tool for reactor simulation, it has the capability of greatly reducing computation time while retaining accuracy of relevant quantities.  The goal of this summary is to demonstrate IQS's performance with multi-physics simulations, as well as techniques to improve its performance.  The technique focused on incorporating a new time scale in IQS for feedback quantities and PRKE parameters.  The results when IQS is applied to the temperature feedback model of the LRA benchmark showed that incorporating a intermediate time scale for temperature has significant impact on IQS performance.

The full paper version will include time adaptive simulations for multiphysics dynamic transients: LRA benchmark, a full core TREAT model, and the Lady Godiva benchmark with structural feedback \cite{CritSafetyHandbook}. Performance of the IQS method with intermediate time scale for physics feedback will be compared to that of an implicit discretization of the flux equations with feedback.
